### 2018-08-23 {{ cookiecutter.repo_name }}/Paper/paper.tex
Added new files to cookiecutter project

\PassOptionsToPackage{pdfpagelabels=false}{hyperref} 
\documentclass[useAMS,usenatbib, usedcolumn]{mnras}
\pdfoutput=1 %for arxiv 
\usepackage{graphicx}
\usepackage{color}
\usepackage{amsmath,amssymb,amstext}
\usepackage[T1]{fontenc}
\usepackage{mathptmx,txfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage[most]{tcolorbox}
\usepackage{ae,aecompl}
\usepackage[normalem]{ulem} % Added by MS for \sout -> not required for final version
\input{hyperlink-year-only-natbib-patch}

\hypersetup{
    pdfauthor={Victor F. Calderon},
    pdftitle={Main title},
    pdfkeywords={cosmology: observations --- cosmology: large-scale structure 
            of Universe --- galaxies: groups --- galaxies:clusters
            --- methods: statistical, machine learning},
    colorlinks=true,
    citecolor=blue,
    linkcolor=magenta,
    % filecolor=magenta,
    urlcolor=cyan}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% ------ Modules ------ %%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{array}
\usepackage{afterpage}
\usepackage{color}
\usepackage{graphicx}
\usepackage{amsmath, amssymb}
\usepackage{soul,xcolor}
\usepackage{epstopdf}
\usepackage{units}
\usepackage{relsize}
\usepackage{enumitem}
\usepackage{url}
\usepackage{appendix}
\usepackage{footnote}
\usepackage{xspace}
\usepackage{float}

\usepackage{booktabs}
\usepackage{tabularx}

\usepackage{color}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{enumitem}
\usepackage{xspace}
\usepackage{float}
\usepackage{booktabs}
\usepackage{tabularx}

\usepackage{relsize}
\usepackage{array}
\usepackage{afterpage}
\usepackage{units}
\usepackage{url}
\usepackage{appendix}
\usepackage{footnote}
\usepackage{natbib}

%%% Graphics path
\graphicspath{{./Figures/}}

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% ------ Commands ------ %%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setstcolor{red}
\definecolor{change}{RGB}{255,3,3}
\def\change {{\color{change}} }
\def\starfpy {\textsc{StarfPy}}
\newcommand{\refsec}[1]{$\S$\ref{#1}}

\newcommand{\msun}{h^{-1}M_\odot}
%\newcommand{\msunh}{\mbox{$h^{-1} \textrm{M}_{\odot}$}}
% \newcommand{\kpch}{\mbox{$\textrm{kpc}/h$}}
\newcommand{\hkpc}{\mbox{$h^{-1}\textrm{kpc}$}}
\newcommand{\hmpc}{\mbox{$h^{-1}\textrm{Mpc}$} }
\newcommand{\kmsMpc}{\mbox{$\textrm{km}\ \textrm{s}^{-1}\ \textrm{Mpc}^{-1}$}}
% \newcommand{\mpch}{\mbox{$\textrm{kpc}/h$}}
% \newcommand{\kms}{$\textrm{km}s^{-1}$}
\newcommand{\hmpcthreeinv}{\mbox{$h^{3} \textrm{Mpc}^{-3}$}}
\newcommand{\mstar}{\mbox{$\textrm{M}_{\star}$}}
\newcommand{\gr}{\ensuremath{(g-r)}\xspace}
\newcommand{\logssfr}{$\log\ \textrm{sSFR}$}
\newcommand{\xirp}{$\xi(r_{p})$}
\newcommand{\rband}{\textit{r}-band}
\newcommand{\gband}{\textit{g}-band }
\newcommand{\bfof}{\texttt{berlind-fof}\xspace}
\newcommand{\MD}[1]{{\texttt Mr#1-SDSS}\xspace}
\newcommand{\MM}[1]{{\texttt Mr#1-Mock}\xspace}
\newcommand{\MR}[1]{{\texttt Mr#1}\xspace}
\newcommand{\Mr}[1]{{Mr#1}\xspace}
\newcommand{\mgroup}{\ensuremath{M_\textrm{group}}\xspace}
\newcommand{\MPA}{MPA-JHU }
\newcommand{\mcf}{\ensuremath{\mathcal{M}(r_{p})}\xspace}
\newcommand{\mcft}{\texorpdfstring{\mcf}{MCF}}
\newcommand{\sersic}{{S\'ersic}\xspace}
% \newcommand{\onehn}{1-halo}
% \newcommand{\twohn}{2-halo}
%
\newcommand{\failval}{-999 }
\newcommand{\ssfr}{{sSFR}\xspace}
\newcommand{\sfr}{{SFR}\xspace}
\newcommand{\lcdm}{{\ensuremath{\Lambda}CDM}\xspace}
\newcommand{\figwidth}{0.47}
\newcommand{\figheight}{0.80}
\newcommand{\catsurl}{\url{https://github.com/vcalderon2009/SDSS_Groups_ML}}
\newcommand{\dsum}{\displaystyle \sum\limits}

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
\input{macros_dc.sty}

% for comments:
%% MS - had to define the color for my edits
\definecolor{orange}{rgb}{1,0.5,0}
\setlength{\marginparwidth}{1.2in}
\let\oldmarginpar\marginpar
\renewcommand\marginpar[1]{\-\oldmarginpar[\raggedleft\footnotesize #1]%
{\raggedright\footnotesize #1}}

%%% Here are the things that make collaborative effort easier
\newcommand{\todo}[1]{\marginpar{\color{red}TODO}{\color{red}#1}}
\newcommand{\ab}[1]{{\color{blue}{\bf AB:} #1}}
\newcommand{\vc}[1]{{\color{cyan}{\bf VC:} #1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%% Citing previous papers
\defcitealias{Calderon2018}{C18}
\defcitealias{Zu2016a}{Zu16}

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title
\title{Prediction of Cluster and Group masses in SDSS DR7 via a machine learning approach}
% Authors
\author[Calderon et al.]{%
Victor F. Calderon$^{1}$\thanks{E-mail:  \mailto{victor.calderon@vanderbilt.edu}},
Andreas A. Berlind$^{1}$\vspace*{0.2em} \\ 
% List of Institutions
$^{1}$Department of Physics and Astronomy, Vanderbilt University, Nashville, TN 37235, USA
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2018}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

\begin{abstract}
We present a machine learning approach (ML) for the prediction of 
Cluster and Group masses with an improved performance over
using conventional methods. We make use of synthetic catalogues
that aim to emulate the clustering of galaxies and joint-distributions
of properties of galaxis in the real Universe in order to train
three ML algorithms to correctly predict cluster and galaxy group masses.
\end{abstract}

\begin{keywords}
cosmology: observations --- cosmology: large-scale structure 
            of Universe --- galaxies: groups --- galaxies:clusters
            --- methods: statistical
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%% ------     Introduction     ------ %%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
\label{sec:intro}

\begin{itemize}[leftmargin=0.5\parindent, labelsep=0.5\parindent]
    \item
    Current literature on previous analyses that have used ML to
    determine masses of galaxy groups and galaxy clusters.

    \item
    How has ML been used before to estimate properties of
    galaxy groups. See `Paul2015'. Also see \citet{Ntampaka2015}.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%% ------     Data     ------ %%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% ============================================ %%%
\section{Data and Methods}
\label{sec:data_meas}

\begin{itemize}[leftmargin=0.5\parindent, labelsep=0.5\parindent]
    \item
    Summarize the different subsections of the \textit{data} main section.

    \item
    Introduce the catalogues presented in \citet{Calderon2018}.
    Especifically \S 2.1 - 2.3.

    \item
    Characterize the different features that we use as part of the ML
    training. Describe in depth the different \textit{features} used.

\end{itemize}

In this section, we present the datasets used throughout this analysis,
and introdue the main machine learning algorithms and statistical
methods that we use to estimate the masses of galaxy groups and galaxy
clusters. In \refsec{subsec:SDSS_galaxy_catalogues}, we briefly describe
the SDSS galaxy sample and mock synthethic galaxy catalogues that we use,
along with the parameters that are included in these catalogue. In
\refsec{subsec:galprop_features}, we introduce the different \textit{features}
that we use for training our ML predictors, and provide a guide on
how these are calculated. Finally, in \refsec{subsec:ml_algorithms} we
provide a brief overview of the different algorithms that we use in
this analysis, as well as the default tuning parameters used by each
algorithm.

%%% ============================================ %%%
%%% --- Galaxy sample and mock galaxy catalogues %%%
%%% ============================================ %%%
\subsection{SDSS Galaxy Sample and Mock Galaxy Catalogues}
\label{subsec:SDSS_galaxy_catalogues}

\begin{itemize}[leftmargin=0.5\parindent, labelsep=0.5\parindent]
    \item
    Introduce the catalogues used in this analysis

    \item
    Reference to \citet{Calderon2018} about the mock catalogues 
    used in this analysis.

    \item
    Briefly mention how galaxy properties are assigned to mock
    galaxies

    \item
    Also mention the \textit{group-finding} step taken for each
    galaxy group.
\end{itemize}

%%% ============================================ %%%
%%% --- SDSS Galaxy Sample                       %%%
%%% ============================================ %%%
\subsubsection{SDSS Galaxy Sample}
\label{subsubsec:NYU_DR7}

%%% ============================================ %%%
%%% --- Mock Galaxy catalogues                   %%%
%%% ============================================ %%%
\subsubsection{Mock Galaxy Catalogues}
\label{subsubsec:Mock_Catls}

%%% ============================================ %%%
%%% --- Galaxy properties as 'features' ---      %%%
%%% ============================================ %%%
\subsection{Galaxy properties as \textit{features}}
\label{subsec:galprop_features}

\begin{itemize}[leftmargin=0.5\parindent, labelsep=0.5\parindent]
    \item
    In this section, I summarize the different \textit{features} used
    during the training of the algorithms.

\end{itemize}

%%% ============================================ %%%
%%% --- Machine Learning algorithms ---          %%%
%%% ============================================ %%%
\subsection{Machine Learning algorithms}
\label{subsec:ml_algorithms}

\begin{itemize}[leftmargin=0.5\parindent, labelsep=0.5\parindent]
    \item
    Talk about the different algorithms, i.e. Random Forest
    \citet{Breiman2001}, XGBoost \citep{Chen2016}.

    \item Have a separate section for each algorithm.
\end{itemize}

%%% ============================================ %%%
%%% --- General Overview section ---             %%%
%%% ============================================ %%%
\subsubsection{General Overview}
\label{subsub:ml_gen_overview}

%%% ============================================ %%%
%%% --- XGBoost section ---                      %%%
%%% ============================================ %%%
\subsubsection{XGBoost}
\label{subsub:ml_xgboost}

%%% ============================================ %%%
%%% --- Random Forests section ---               %%%
%%% ============================================ %%%
\subsubsection{Random Forest}
\label{subsub:ml_random_forest}

%%% ============================================ %%%
%%% --- Neural network section ---               %%%
%%% ============================================ %%%
\subsubsection{Neural network}
\label{subsub:ml_neural_network}

%%% ============================================ %%%
%%% --- Results ---                              %%%
%%% ============================================ %%%
\section{Results}
\label{sec:results}

\begin{itemize}[leftmargin=0.5\parindent, labelsep=0.5\parindent]
    \item
    Include reference to \citet{Ivezic2014}

    \item
    Section on the different metrics used to evaluate how well the
    algorithms are performing.

    \item
    Section on the different types of predictions for the different
    types of models, i.e. different \textit{velocity bias} ($\sigma_{v}$)
    and different \textit{HOD} models at fixed $\sigma_{v}$.
\end{itemize}

In this section, we present the results of the mass predictions for
galaxy groups and galaxy clusters of SDSS DR7.

%%% ============================================ %%%
%%% --- Results --- Fixed HOD and Velocity Bias  %%%
%%% ============================================ %%%
\subsection{Fixed HOD and Velocity bias}
\label{subsec:fixed_hod_dv}

%%% ============================================ %%%
%%% --- Results --- Varying HOD models  %%%
%%% ============================================ %%%
\subsection{Variations of HOD and Velocity Bias}
\label{subsec:hod_dv_variations}

%%% ============================================ %%%
%%% --- Results --- Varying HOD models  %%%
%%% ============================================ %%%
\subsubsection{Varying HOD models}
\label{subsubsec:fixed_dv_only}

%%% ============================================ %%%
%%% --- Results --- Varying HOD models  %%%
%%% ============================================ %%%
\subsubsection{Varying Velocity bias models}
\label{subsubsec:fixed_HOD_only}

%%% ============================================ %%%
\section{Summary and Discussion}\label{sec:summary_discussion}

\begin{itemize}[leftmargin=0.5\parindent, labelsep=0.5\parindent]
    \item
    Summarize all of the findings.

    \item
    Mention the website, at which the catalogues can be found.

\end{itemize}

%%% ============================================ %%%
\section{Acknowledgements}\label{sec:acknowledments}

The mock catalogues used in this paper were produced by the LasDamas project 
(\url{http://lss.phy.vanderbilt.edu/lasdamas/}); we thank NSF XSEDE for 
providing the computational resources for LasDamas. Some of the 
computational facilities used in this project were provided by the 
Vanderbilt Advanced Computing Center for Research and Education (ACCRE). 
This project has been supported by the National Science Foundation (NSF) 
through a Career Award (AST-1151650). 
Parts of this research were conducted by the Australian Research Council 
Centre of Excellence for All Sky Astrophysics in 3 Dimensions (ASTRO 3D), 
through project number CE170100013.
This research has made use of 
NASA's Astrophysics Data System. This work made use of the IPython package 
\citep{Perez2007}, Scikit-learn \citep{McKinney2010}, SciPy 
\citep{jones_scipy_2001}, matplotlib, a Python library for publication 
quality graphics \citep{Hunter:2007}, Astropy, a community-developed 
core Python package for Astronomy \citep{AstropyCollaboration2013}, and 
NumPy \citep{VanDerWalt2011}. Funding for the SDSS and SDSS-II has been 
provided by the Alfred P. Sloan Foundation, the Participating Institutions, 
the National Science Foundation, the U.S. Department of Energy, 
the National Aeronautics and Space Administration, the 
Japanese Monbukagakusho, the Max Planck Society, and the Higher Education 
Funding Council for England. The SDSS Web Site is http://www.sdss.org/. 
The SDSS is managed by the Astrophysical Research Consortium for the 
Participating Institutions. The Participating Institutions are the 
American Museum of Natural History, Astrophysical Institute Potsdam, 
University of Basel, University of Cambridge, Case Western Reserve 
University, University of Chicago, Drexel University, Fermilab, the 
Institute for Advanced Study, the Japan Participation Group, 
Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, 
the Kavli Institute for Particle Astrophysics and Cosmology, 
the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), 
Los Alamos National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), 
the Max-Planck-Institute for Astrophysics (MPA), 
New Mexico State University, Ohio State University, 
University of Pittsburgh, University of Portsmouth, Princeton University, 
the United States Naval Observatory, and the University of Washington. 
These acknowledgements were compiled using the Astronomy Acknowledgement 
Generator.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%% ------     Bibliography     ------ %%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \bibliographystyle{mn2e}
\bibliographystyle{mnras}
\bibliography{Mendeley}

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

### 2018-08-24 {{ cookiecutter.repo_name }}/Paper/paper.tex
Updated section of paper template. Included style files, and modified the main structure of the paper template.

@@
+%%
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%% Main MNRAS template for Cookicutter project
+%%
+%% Author: Victor F. Calderon (http://vcalderon.me)
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%% ========== PREAMBLE ========== %%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\listfiles
 \PassOptionsToPackage{pdfpagelabels=false}{hyperref}
 \documentclass[useAMS,usenatbib, usedcolumn]{mnras}
-\pdfoutput=1 %for arxiv 
-\usepackage{graphicx}
-\usepackage{color}
-\usepackage{amsmath,amssymb,amstext}
-\usepackage[T1]{fontenc}
-\usepackage{mathptmx,txfonts}
-\usepackage[figure,figure*]{hypcap}
-\usepackage[most]{tcolorbox}
-\usepackage{ae,aecompl}
-\usepackage[normalem]{ulem} % Added by MS for \sout -> not required for final version
-\input{hyperlink-year-only-natbib-patch}
+\pdfoutput=1 %% Used by arXiv
 
+%% Include all packages
+\input{../Extras/packages}
+
+%% Include all commands
+\input{../Extras/commands}
+
+%% Include script to fix bibliography
+\input{../Script_files/hyperlink-year-only-natbib-patch.tex}
+
+%% Program-specific configuration
+% PDF settings
 \hypersetup{
-    pdfauthor={Victor F. Calderon},
-    pdftitle={Main title},
+    pdfauthor={{ cookiecutter.author_first_name + '_' + cookiecutter.author_last_name}},
+    pdftitle={{ cookiecutter.paper_title}},
     pdfkeywords={cosmology: observations --- cosmology: large-scale structure 
@@
     linkcolor=magenta,
-    % filecolor=magenta,
-    urlcolor=cyan}
+    urlcolor=cyan
+}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%% ------ Modules ------ %%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
-\usepackage{array}
-\usepackage{afterpage}
-\usepackage{color}
-\usepackage{graphicx}
-\usepackage{amsmath, amssymb}
-\usepackage{soul,xcolor}
-\usepackage{epstopdf}
-\usepackage{units}
-\usepackage{relsize}
-\usepackage{enumitem}
-\usepackage{url}
-\usepackage{appendix}
-\usepackage{footnote}
-\usepackage{xspace}
-\usepackage{float}
+% Graphics path
+\graphicspath{{../Figures/}}
 
-\usepackage{booktabs}
-\usepackage{tabularx}
-
-\usepackage{color}
-\usepackage{graphicx}
-\usepackage{epstopdf}
-\usepackage{enumitem}
-\usepackage{xspace}
-\usepackage{float}
-\usepackage{booktabs}
-\usepackage{tabularx}
-
-\usepackage{relsize}
-\usepackage{array}
-\usepackage{afterpage}
-\usepackage{units}
-\usepackage{url}
-\usepackage{appendix}
-\usepackage{footnote}
-\usepackage{natbib}
-
-%%% Graphics path
-\graphicspath{{./Figures/}}
-
+%% Column-specific
 \newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%% ------ Commands ------ %%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\setstcolor{red}
-\definecolor{change}{RGB}{255,3,3}
-\def\change {{\color{change}} }
-\def\starfpy {\textsc{StarfPy}}
-\newcommand{\refsec}[1]{$\S$\ref{#1}}
+%% Citation aliases
+%% - In here, you can add an alias to a specific citation
+%%
+%% Example:
+%%      \defcitealias{citation_key}{alias}
 
-\newcommand{\msun}{h^{-1}M_\odot}
-%\newcommand{\msunh}{\mbox{$h^{-1} \textrm{M}_{\odot}$}}
-% \newcommand{\kpch}{\mbox{$\textrm{kpc}/h$}}
-\newcommand{\hkpc}{\mbox{$h^{-1}\textrm{kpc}$}}
-\newcommand{\hmpc}{\mbox{$h^{-1}\textrm{Mpc}$} }
-\newcommand{\kmsMpc}{\mbox{$\textrm{km}\ \textrm{s}^{-1}\ \textrm{Mpc}^{-1}$}}
-% \newcommand{\mpch}{\mbox{$\textrm{kpc}/h$}}
-% \newcommand{\kms}{$\textrm{km}s^{-1}$}
-\newcommand{\hmpcthreeinv}{\mbox{$h^{3} \textrm{Mpc}^{-3}$}}
-\newcommand{\mstar}{\mbox{$\textrm{M}_{\star}$}}
-\newcommand{\gr}{\ensuremath{(g-r)}\xspace}
-\newcommand{\logssfr}{$\log\ \textrm{sSFR}$}
-\newcommand{\xirp}{$\xi(r_{p})$}
-\newcommand{\rband}{\textit{r}-band}
-\newcommand{\gband}{\textit{g}-band }
-\newcommand{\bfof}{\texttt{berlind-fof}\xspace}
-\newcommand{\MD}[1]{{\texttt Mr#1-SDSS}\xspace}
-\newcommand{\MM}[1]{{\texttt Mr#1-Mock}\xspace}
-\newcommand{\MR}[1]{{\texttt Mr#1}\xspace}
-\newcommand{\Mr}[1]{{Mr#1}\xspace}
-\newcommand{\mgroup}{\ensuremath{M_\textrm{group}}\xspace}
-\newcommand{\MPA}{MPA-JHU }
-\newcommand{\mcf}{\ensuremath{\mathcal{M}(r_{p})}\xspace}
-\newcommand{\mcft}{\texorpdfstring{\mcf}{MCF}}
-\newcommand{\sersic}{{S\'ersic}\xspace}
-% \newcommand{\onehn}{1-halo}
-% \newcommand{\twohn}{2-halo}
-%
-\newcommand{\failval}{-999 }
-\newcommand{\ssfr}{{sSFR}\xspace}
-\newcommand{\sfr}{{SFR}\xspace}
-\newcommand{\lcdm}{{\ensuremath{\Lambda}CDM}\xspace}
-\newcommand{\figwidth}{0.47}
-\newcommand{\figheight}{0.80}
-\newcommand{\catsurl}{\url{https://github.com/vcalderon2009/SDSS_Groups_ML}}
-\newcommand{\dsum}{\displaystyle \sum\limits}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%% ========== Title Page ========== %%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% Please keep new commands to a minimum, and use \newcommand not \def to avoid
-% overwriting existing commands. Example:
-%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
-\input{macros_dc.sty}
+%% Paper title
+\title{{ cookiecutter.paper_title}}
 
-% for comments:
-%% MS - had to define the color for my edits
-\definecolor{orange}{rgb}{1,0.5,0}
-\setlength{\marginparwidth}{1.2in}
-\let\oldmarginpar\marginpar
-\renewcommand\marginpar[1]{\-\oldmarginpar[\raggedleft\footnotesize #1]%
-{\raggedright\footnotesize #1}}
-
-%%% Here are the things that make collaborative effort easier
-\newcommand{\todo}[1]{\marginpar{\color{red}TODO}{\color{red}#1}}
-\newcommand{\ab}[1]{{\color{blue}{\bf AB:} #1}}
-\newcommand{\vc}[1]{{\color{cyan}{\bf VC:} #1}}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%% Citing previous papers
-\defcitealias{Calderon2018}{C18}
-\defcitealias{Zu2016a}{Zu16}
-
-%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
-
-% Title
-\title{Prediction of Cluster and Group masses in SDSS DR7 via a machine learning approach}
-% Authors
-\author[Calderon et al.]{%
-Victor F. Calderon$^{1}$\thanks{E-mail:  \mailto{victor.calderon@vanderbilt.edu}},
-Andreas A. Berlind$^{1}$\vspace*{0.2em} \\ 
-% List of Institutions
-$^{1}$Department of Physics and Astronomy, Vanderbilt University, Nashville, TN 37235, USA
+%% Author
+\author[{{ cookiecutter.author_last_name + 'et al. ' + cookiecutter.paper_pubyear}}]{%
+    %% Author List
+    %%
+    {{ cookiecutter.author_first_name + '_' + cookiecutter.author_last_name }}$^{1}$\thanks{Email: \mailto{ {{cookiecutter.author_email}} }}\\
+    %% 
+    %% List of Institutions
+    $^{1}$ {{ cookiecutter.author_affiliation }}
 }
 
-% These dates will be filled out by the publisher
+%%% These daets will be filled out by the publisher
 \date{Accepted XXX. Received YYY; in original form ZZZ}
 
-% Enter the current year, for the copyright statements etc.
-\pubyear{2018}
+%% Publication year
+%% -- Enter the current year, for the copyright statements, etc.
+\pubyear{ {{ cookiecutter.paper_pubyear}}}
 
-% Don't change these lines
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%% ========== Starting document ========== %%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Don't change these lines
 \begin{document}
+
+% Defining color
+\setstcolor{red}
 \label{firstpage}
@@
 
-\begin{abstract}
-We present a machine learning approach (ML) for the prediction of 
-Cluster and Group masses with an improved performance over
-using conventional methods. We make use of synthetic catalogues
-that aim to emulate the clustering of galaxies and joint-distributions
-of properties of galaxis in the real Universe in order to train
-three ML algorithms to correctly predict cluster and galaxy group masses.
-\end{abstract}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%% ========== Abstract ========== %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\begin{keywords}
-cosmology: observations --- cosmology: large-scale structure 
-            of Universe --- galaxies: groups --- galaxies:clusters
-            --- methods: statistical
-\end{keywords}
+\input{../Section_files/01_abstract.tex}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%% ------     Introduction     ------ %%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%% ========== Introduction ========== %%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Introduction}
-\label{sec:intro}
+\input{../Section_files/02_introduction.tex}
 
-\begin{itemize}[leftmargin=0.5\parindent, labelsep=0.5\parindent]
-    \item
-    Current literature on previous analyses that have used ML to
-    determine masses of galaxy groups and galaxy clusters.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%% ========== Data and Methods ========== %%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-    \item
-    How has ML been used before to estimate properties of
-    galaxy groups. See `Paul2015'. Also see \citet{Ntampaka2015}.
+\input{../Section_files/03_data_methods.tex}
 
-\end{itemize}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%% ========== Results ========== %%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%% ------     Data     ------ %%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\input{../Section_files/04_results.tex}
 
-%%% ============================================ %%%
-\section{Data and Methods}
-\label{sec:data_meas}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%% ========== Summary and Discussion ========== %%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\begin{itemize}[leftmargin=0.5\parindent, labelsep=0.5\parindent]
-    \item
-    Summarize the different subsections of the \textit{data} main section.
+\input{../Section_files/05_summary_discussion.tex}
 
-    \item
-    Introduce the catalogues presented in \citet{Calderon2018}.
-    Especifically \S 2.1 - 2.3.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%% ========== Acknowledgements ========== %%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-    \item
-    Characterize the different features that we use as part of the ML
-    training. Describe in depth the different \textit{features} used.
+\input{../Section_files/06_acknowledgements.tex}
 
-\end{itemize}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%% ========== Bibliography ========== %%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-In this section, we present the datasets used throughout this analysis,
-and introdue the main machine learning algorithms and statistical
-methods that we use to estimate the masses of galaxy groups and galaxy
-clusters. In \refsec{subsec:SDSS_galaxy_catalogues}, we briefly describe
-the SDSS galaxy sample and mock synthethic galaxy catalogues that we use,
-along with the parameters that are included in these catalogue. In
-\refsec{subsec:galprop_features}, we introduce the different \textit{features}
-that we use for training our ML predictors, and provide a guide on
-how these are calculated. Finally, in \refsec{subsec:ml_algorithms} we
-provide a brief overview of the different algorithms that we use in
-this analysis, as well as the default tuning parameters used by each
-algorithm.
-
-%%% ============================================ %%%
-%%% --- Galaxy sample and mock galaxy catalogues %%%
-%%% ============================================ %%%
-\subsection{SDSS Galaxy Sample and Mock Galaxy Catalogues}
-\label{subsec:SDSS_galaxy_catalogues}
-
-\begin{itemize}[leftmargin=0.5\parindent, labelsep=0.5\parindent]
-    \item
-    Introduce the catalogues used in this analysis
-
-    \item
-    Reference to \citet{Calderon2018} about the mock catalogues 
-    used in this analysis.
-
-    \item
-    Briefly mention how galaxy properties are assigned to mock
-    galaxies
-
-    \item
-    Also mention the \textit{group-finding} step taken for each
-    galaxy group.
-\end{itemize}
-
-%%% ============================================ %%%
-%%% --- SDSS Galaxy Sample                       %%%
-%%% ============================================ %%%
-\subsubsection{SDSS Galaxy Sample}
-\label{subsubsec:NYU_DR7}
-
-%%% ============================================ %%%
-%%% --- Mock Galaxy catalogues                   %%%
-%%% ============================================ %%%
-\subsubsection{Mock Galaxy Catalogues}
-\label{subsubsec:Mock_Catls}
-
-%%% ============================================ %%%
-%%% --- Galaxy properties as 'features' ---      %%%
-%%% ============================================ %%%
-\subsection{Galaxy properties as \textit{features}}
-\label{subsec:galprop_features}
-
-\begin{itemize}[leftmargin=0.5\parindent, labelsep=0.5\parindent]
-    \item
-    In this section, I summarize the different \textit{features} used
-    during the training of the algorithms.
-
-\end{itemize}
-
-%%% ============================================ %%%
-%%% --- Machine Learning algorithms ---          %%%
-%%% ============================================ %%%
-\subsection{Machine Learning algorithms}
-\label{subsec:ml_algorithms}
-
-\begin{itemize}[leftmargin=0.5\parindent, labelsep=0.5\parindent]
-    \item
-    Talk about the different algorithms, i.e. Random Forest
-    \citet{Breiman2001}, XGBoost \citep{Chen2016}.
-
-    \item Have a separate section for each algorithm.
-\end{itemize}
-
-%%% ============================================ %%%
-%%% --- General Overview section ---             %%%
-%%% ============================================ %%%
-\subsubsection{General Overview}
-\label{subsub:ml_gen_overview}
-
-%%% ============================================ %%%
-%%% --- XGBoost section ---                      %%%
-%%% ============================================ %%%
-\subsubsection{XGBoost}
-\label{subsub:ml_xgboost}
-
-%%% ============================================ %%%
-%%% --- Random Forests section ---               %%%
-%%% ============================================ %%%
-\subsubsection{Random Forest}
-\label{subsub:ml_random_forest}
-
-%%% ============================================ %%%
-%%% --- Neural network section ---               %%%
-%%% ============================================ %%%
-\subsubsection{Neural network}
-\label{subsub:ml_neural_network}
-
-%%% ============================================ %%%
-%%% --- Results ---                              %%%
-%%% ============================================ %%%
-\section{Results}
-\label{sec:results}
-
-\begin{itemize}[leftmargin=0.5\parindent, labelsep=0.5\parindent]
-    \item
-    Include reference to \citet{Ivezic2014}
-
-    \item
-    Section on the different metrics used to evaluate how well the
-    algorithms are performing.
-
-    \item
-    Section on the different types of predictions for the different
-    types of models, i.e. different \textit{velocity bias} ($\sigma_{v}$)
-    and different \textit{HOD} models at fixed $\sigma_{v}$.
-\end{itemize}
-
-In this section, we present the results of the mass predictions for
-galaxy groups and galaxy clusters of SDSS DR7.
-
-%%% ============================================ %%%
-%%% --- Results --- Fixed HOD and Velocity Bias  %%%
-%%% ============================================ %%%
-\subsection{Fixed HOD and Velocity bias}
-\label{subsec:fixed_hod_dv}
-
-%%% ============================================ %%%
-%%% --- Results --- Varying HOD models  %%%
-%%% ============================================ %%%
-\subsection{Variations of HOD and Velocity Bias}
-\label{subsec:hod_dv_variations}
-
-%%% ============================================ %%%
-%%% --- Results --- Varying HOD models  %%%
-%%% ============================================ %%%
-\subsubsection{Varying HOD models}
-\label{subsubsec:fixed_dv_only}
-
-%%% ============================================ %%%
-%%% --- Results --- Varying HOD models  %%%
-%%% ============================================ %%%
-\subsubsection{Varying Velocity bias models}
-\label{subsubsec:fixed_HOD_only}
-
-%%% ============================================ %%%
-\section{Summary and Discussion}\label{sec:summary_discussion}
-
-\begin{itemize}[leftmargin=0.5\parindent, labelsep=0.5\parindent]
-    \item
-    Summarize all of the findings.
-
-    \item
-    Mention the website, at which the catalogues can be found.
-
-\end{itemize}
-
-%%% ============================================ %%%
-\section{Acknowledgements}\label{sec:acknowledments}
-
-The mock catalogues used in this paper were produced by the LasDamas project 
-(\url{http://lss.phy.vanderbilt.edu/lasdamas/}); we thank NSF XSEDE for 
-providing the computational resources for LasDamas. Some of the 
-computational facilities used in this project were provided by the 
-Vanderbilt Advanced Computing Center for Research and Education (ACCRE). 
-This project has been supported by the National Science Foundation (NSF) 
-through a Career Award (AST-1151650). 
-Parts of this research were conducted by the Australian Research Council 
-Centre of Excellence for All Sky Astrophysics in 3 Dimensions (ASTRO 3D), 
-through project number CE170100013.
-This research has made use of 
-NASA's Astrophysics Data System. This work made use of the IPython package 
-\citep{Perez2007}, Scikit-learn \citep{McKinney2010}, SciPy 
-\citep{jones_scipy_2001}, matplotlib, a Python library for publication 
-quality graphics \citep{Hunter:2007}, Astropy, a community-developed 
-core Python package for Astronomy \citep{AstropyCollaboration2013}, and 
-NumPy \citep{VanDerWalt2011}. Funding for the SDSS and SDSS-II has been 
-provided by the Alfred P. Sloan Foundation, the Participating Institutions, 
-the National Science Foundation, the U.S. Department of Energy, 
-the National Aeronautics and Space Administration, the 
-Japanese Monbukagakusho, the Max Planck Society, and the Higher Education 
-Funding Council for England. The SDSS Web Site is http://www.sdss.org/. 
-The SDSS is managed by the Astrophysical Research Consortium for the 
-Participating Institutions. The Participating Institutions are the 
-American Museum of Natural History, Astrophysical Institute Potsdam, 
-University of Basel, University of Cambridge, Case Western Reserve 
-University, University of Chicago, Drexel University, Fermilab, the 
-Institute for Advanced Study, the Japan Participation Group, 
-Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, 
-the Kavli Institute for Particle Astrophysics and Cosmology, 
-the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), 
-Los Alamos National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), 
-the Max-Planck-Institute for Astrophysics (MPA), 
-New Mexico State University, Ohio State University, 
-University of Pittsburgh, University of Portsmouth, Princeton University, 
-the United States Naval Observatory, and the University of Washington. 
-These acknowledgements were compiled using the Astronomy Acknowledgement 
-Generator.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%% ------     Bibliography     ------ %%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \bibliographystyle{mn2e}
 \bibliographystyle{mnras}
 \bibliography{Mendeley}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%% ========== End of document ========== %%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2018-08-24 {{ cookiecutter.repo_name }}/Section_files/06_acknowledgements.tex
Updated section of paper template. Included style files, and modified the main structure of the paper template.

%%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Main MNRAS template for Cookicutter project
%%
%% Section -- ACKWNOLEDGEMENTS
%%
%% Author: Victor F. Calderon (http://vcalderon.me)
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% In here, you will add the 'abstract' of your paper

\section{Acknowledgements}
\label{sec:acknowledgements}

This is where the acknowledgements go.
It is useful to use \textbf{Acknowledgement Generator} (\https{https://astrofrog.github.io/acknowledgment-generator/}) to create your
acknowledgements. This lets you add the bibitem entried for each of the
packages used in the analysis.

### 2018-08-24 hooks/post_gen_project.py
Updated pre- and post-cookiecutter tests

@@ -16,7 +16,6 @@ def copy_file(original_filepath, new_filepath):
     shutil.copyfile(os.path.join(PROJECT_DIRECTORY, original_filepath),
                     os.path.join(PROJECT_DIRECTORY, new_filepath))
 
-
 PROJECT_DIRECTORY = os.path.realpath(os.path.curdir)
 
 license_files = {"BSD 3-Clause": 'BSD3.rst',
@@ -24,7 +23,6 @@ license_files = {"BSD 3-Clause": 'BSD3.rst',
                  "Apache Software Licence 2.0": 'APACHE2.rst',
                  "BSD 2-Clause": 'BSD2.rst',
                  "MIT": 'MIT.rst'}
-
 
 def process_licence(licence_name):
     """
@@ -42,21 +40,7 @@ def process_licence(licence_name):
     ## Remove `licenses` folder
     shutil.rmtree(os.path.join(PROJECT_DIRECTORY, 'licenses'))
 
-def process_conf_docs():
-    """
-    Selects the correct `conf.py` file for the project documentation.
-    """
-    if '{{ cookiecutter.use_astropy_theme_or_RTD }}' == 'RTD':
-        shutil.copyfile(os.path.join(PROJECT_DIRECTORY, 'docs', 'read_docs', 'conf_rtd.py'),
-                        os.path.join(PROJECT_DIRECTORY, 'docs', 'conf.py'))
-    if '{{ cookiecutter.use_astropy_theme_or_RTD }}' == 'Astropy':
-        shutil.copyfile(os.path.join(PROJECT_DIRECTORY, 'docs', 'read_docs', 'conf_astropy.py'),
-                        os.path.join(PROJECT_DIRECTORY, 'docs', 'conf.py'))
-    ##
-    ## Removing `read_docs` folder
-    shutil.rmtree(os.path.join(PROJECT_DIRECTORY, 'docs','read_docs'))
-
-
+# Running command
 if __name__ == '__main__':
 
     process_licence('{{ cookiecutter.open_source_license }}')
@@ -68,9 +52,6 @@ if __name__ == '__main__':
         remove_file('.rtd-environment.yml')
         remove_file('readthedocs.yml')
     ##
-    ## Documentation
-    process_conf_docs()
-    ##
     ## Astropy Helpers
     try:
         from git import Repo
@@ -78,21 +59,9 @@ if __name__ == '__main__':
         new_repo = Repo.init(PROJECT_DIRECTORY)
         new_repo.git.add('.')
[…]

### 2018-08-24 tests/test_creation.py

@@ -30,6 +30,38 @@ def default_baked_project(tmpdir):
     # cleanup after
     shutil.rmtree(out_dir)
 
+##
+## Testing for FILE existence
+##
+def test_gitignore(default_baked_project):
+    makefile_path = os.path.join(default_baked_project, '.gitignore')
+
+    assert os.path.exists(makefile_path)
+    assert no_curlies(makefile_path)
+
+def test_makefile(default_baked_project):
+    makefile_path = os.path.join(default_baked_project, 'Makefile')
+
+    assert os.path.exists(makefile_path)
+    assert no_curlies(makefile_path)
+
+def test_makefile_inc(default_baked_project):
+    makefile_path = os.path.join(default_baked_project, 'Makefile.inc')
+
+    assert os.path.exists(makefile_path)
+    assert no_curlies(makefile_path)
+
+def test_bibliography(default_baked_project):
+    reqs_path = os.path.join(default_baked_project, 'Mendeley.bib')
+
+    assert os.path.exists(reqs_path)
+    assert no_curlies(reqs_path)
+
+def test_license(default_baked_project):
+    license_path = os.path.join(default_baked_project, 'LICENSE')
+
+    assert os.path.exists(license_path)
+    assert no_curlies(license_path)
 
 def test_readme(default_baked_project):
     readme_path = os.path.join(default_baked_project, 'README.md')
@@ -38,45 +70,24 @@ def test_readme(default_baked_project):
     assert no_curlies(readme_path)
 
 
-def test_license(default_baked_project):
-    license_path = os.path.join(default_baked_project, 'LICENSE')
-
-    assert os.path.exists(license_path)
-    assert no_curlies(license_path)
-
-
 def test_requirements(default_baked_project):
     reqs_path = os.path.join(default_baked_project, 'requirements.txt')
 
     assert os.path.exists(reqs_path)
     assert no_curlies(reqs_path)
 
-
-def test_makefile(default_baked_project):
-    makefile_path = os.path.join(default_baked_project, 'Makefile')
-
-    assert os.path.exists(makefile_path)
-    assert no_curlies(makefile_path)
-
+##
+## Testing for FOLDER existence
+##
 
 def test_folders(default_baked_project):
     expected_dirs = [
-        'data',
-        os.path.join('data', 'external'),
-        os.path.join('data', 'interim'),
-        os.path.join('data', 'processed'),
-        os.path.join('data', 'raw'),
-        'docs',
-        'models',
-        'notebooks',
[…]

### 2018-08-24 tests/test_creation.py
Moved around MNRAS bibliography style and class files

@@ -86,8 +86,7 @@ def test_folders(default_baked_project):
         'Figures',
         'Paper',
         'Script_files',
-        'Section_files',
-        'Style_files'
+        'Section_files'
     ]
 
     ignored_dirs = [

### 2018-08-24 {{ cookiecutter.repo_name }}/Paper/paper.tex
Modified 'Figures' path
Deleted 'column-specific' settings
Trying to correct jinga2 with braces error

@@
 % Graphics path
-\graphicspath{{../Figures/}}
+\graphicspath{../Figures/}
 
 %% Column-specific
-\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
-\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
-\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
 
@@
 %% Author
-\author[{{ cookiecutter.author_last_name + 'et al. ' + cookiecutter.paper_pubyear}}]{%
-    %% Author List
-    %%
+\author[{{ cookiecutter.author_last_name + 'et al. ' + cookiecutter.paper_pubyear}}]{
+    % Author List
     {{ cookiecutter.author_first_name + '_' + cookiecutter.author_last_name }}$^{1}$\thanks{Email: \mailto{ {{cookiecutter.author_email}} }}\\
-    %% 
-    %% List of Institutions
     $^{1}$ {{ cookiecutter.author_affiliation }}

### 2018-08-24 hooks/post_gen_project.py
Removed 'use_travis_ci' from script

@@ -44,15 +44,8 @@ def process_licence(licence_name):
 if __name__ == '__main__':
 
     process_licence('{{ cookiecutter.open_source_license }}')
-
-    if '{{ cookiecutter.use_travis_ci }}' != 'y':
-        remove_file('.travis.yml')
-
-    if '{{ cookiecutter.use_read_the_docs }}' != 'y':
-        remove_file('.rtd-environment.yml')
-        remove_file('readthedocs.yml')
     ##
-    ## Astropy Helpers
+    ## Initializing repository
     try:
         from git import Repo
 

### 2018-08-24 {{ cookiecutter.repo_name }}/Paper/paper.tex
Updated with changes using Overleaf

@@
 %% Paper title
-\title{{ cookiecutter.paper_title}}
+\title{ {{ cookiecutter.paper_title}}}
 
@@
     % Author List
-    {{ cookiecutter.author_first_name + '_' + cookiecutter.author_last_name }}$^{1}$\thanks{Email: \mailto{ {{cookiecutter.author_email}} }}\\
-    $^{1}$ {{ cookiecutter.author_affiliation }}
+    {{ cookiecutter.author_first_name + '_' + cookiecutter.author_last_name }}$^{1}$\thanks{Email: \mailto{{{cookiecutter.author_email}}}}\\
+    $^{1}$ {{ cookiecutter.author_affiliation}}
 }
@@
 %% -- Enter the current year, for the copyright statements, etc.
-\pubyear{ {{ cookiecutter.paper_pubyear}}}
+\pubyear{{{ cookiecutter.paper_pubyear}}}
 

### 2018-08-24 {{ cookiecutter.repo_name }}/Section_files/06_acknowledgements.tex
Updated with changes using Overleaf

@@
 This is where the acknowledgements go.
-It is useful to use \textbf{Acknowledgement Generator} (\https{https://astrofrog.github.io/acknowledgment-generator/}) to create your
+It is useful to use \textbf{Acknowledgement Generator} (\https{astrofrog.github.io/acknowledgment-generator/}) to create your
 acknowledgements. This lets you add the bibitem entried for each of the
 packages used in the analysis.
+
+The mock catalogues used in this paper were produced by the LasDamas project 
+(\url{http://lss.phy.vanderbilt.edu/lasdamas/}); we thank NSF XSEDE for 
+providing the computational resources for LasDamas. Some of the 
+computational facilities used in this project were provided by the 
+Vanderbilt Advanced Computing Center for Research and Education (ACCRE). 
+This project has been supported by the National Science Foundation (NSF) 
+through a Career Award (AST-1151650). 
+Parts of this research were conducted by the Australian Research Council 
+Centre of Excellence for All Sky Astrophysics in 3 Dimensions (ASTRO 3D), 
+through project number CE170100013.
+This research has made use of 
+NASA's Astrophysics Data System. This work made use of the IPython package 
+\citep{Perez2007}, Scikit-learn \citep{McKinney2010}, SciPy 
+\citep{jones_scipy_2001}, matplotlib, a Python library for publication 
+quality graphics \citep{Hunter:2007}, Astropy, a community-developed 
+core Python package for Astronomy \citep{AstropyCollaboration2013}, and 
+NumPy \citep{VanDerWalt2011}. Funding for the SDSS and SDSS-II has been 
+provided by the Alfred P. Sloan Foundation, the Participating Institutions, 
+the National Science Foundation, the U.S. Department of Energy, 
+the National Aeronautics and Space Administration, the 
+Japanese Monbukagakusho, the Max Planck Society, and the Higher Education 
+Funding Council for England. The SDSS Web Site is http://www.sdss.org/. 
+The SDSS is managed by the Astrophysical Research Consortium for the 
+Participating Institutions. The Participating Institutions are the 
+American Museum of Natural History, Astrophysical Institute Potsdam, 
+University of Basel, University of Cambridge, Case Western Reserve 
+University, University of Chicago, Drexel University, Fermilab, the 
+Institute for Advanced Study, the Japan Participation Group, 
+Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, 
+the Kavli Institute for Particle Astrophysics and Cosmology, 
+the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), 
+Los Alamos National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), 
+the Max-Planck-Institute for Astrophysics (MPA), 
+New Mexico State University, Ohio State University, 
+University of Pittsburgh, University of Portsmouth, Princeton University, 
+the United States Naval Observatory, and the University of Washington. 
+These acknowledgements were compiled using the Astronomy Acknowledgement 
+Generator.

### 2018-08-24 {{ cookiecutter.repo_name }}/Paper/paper.tex
Updated files for the Cookiecutter in general
Fixing jinja2 error with extra curly braces
Trying to remove annoying curly brackets

@@
 %% Paper title
-\title{ {{ cookiecutter.paper_title}}}
+\title{ {{ cookiecutter.paper_title}} }
 
@@
     % Author List
-    {{ cookiecutter.author_first_name + '_' + cookiecutter.author_last_name }}$^{1}$\thanks{Email: \mailto{{{cookiecutter.author_email}}}}\\
+    {{ cookiecutter.author_first_name + '_' + cookiecutter.author_last_name }}$^{1}$\thanks{Email: \mailto{ {{cookiecutter.author_email}} }}\\
     $^{1}$ {{ cookiecutter.author_affiliation}}

### 2018-08-24 {{ cookiecutter.repo_name }}/Paper/paper.tex
Annoying curly brackets
Trying to fix issue

@@
     % Author List
-    {{ cookiecutter.author_first_name + '_' + cookiecutter.author_last_name }}$^{1}$\thanks{Email: \mailto{ {{cookiecutter.author_email}} }}\\
+    {{ cookiecutter.author_name }}$^{1}$\thanks{Email: \mailto{{{ cookiecutter.author_email }}}}\\
     $^{1}$ {{ cookiecutter.author_affiliation}}
@@
 %% -- Enter the current year, for the copyright statements, etc.
-\pubyear{{{ cookiecutter.paper_pubyear}}}
+\pubyear{ {{ cookiecutter.paper_pubyear}} }
 
@@
 \bibliographystyle{mnras}
-\bibliography{Mendeley}
+\bibliography{Mendeley.bib}
 

### 2018-08-24 {{ cookiecutter.repo_name }}/Paper/paper.tex
Added spaces
Trying new syntax

@@
     % Author List
-    {{ cookiecutter.author_name }}$^{1}$\thanks{Email: \mailto{{{ cookiecutter.author_email }}}}\\
+    {{ cookiecutter.author_name }}$^{1}$\thanks{Email: \href{mailto:{{ cookiecutter.author_email }}}{ {{ cookiecutter.author_email }} } }\\
     $^{1}$ {{ cookiecutter.author_affiliation}}

### 2018-08-25 docs/conf.py
Updated banner in docs

@@ -105,8 +105,8 @@ release = setup_cfg['version']
 
 # Please update these texts to match the name of your package.
 html_theme_options = {
-    'logotext1': 'package',  # white,  semi-bold
-    'logotext2': '-template',  # orange, light
+    'logotext1': 'MNRAS',  # white,  semi-bold
+    'logotext2': '-cookiecutter',  # orange, light
     'logotext3': ':docs'   # white,  light
     }
 

### 2018-08-26 {{ cookiecutter.repo_name }}/Paper/paper.tex
Fixed error with underscore symbold. Reference: https://tex.stackexchange.com/questions/53399/is-it-necessary-to-escape-underscores-in-href-with-dollar-signs-or

--- 2018-08-24 {{ cookiecutter.repo_name }}/Paper/paper.tex
@@
     % Author List
-    {{ cookiecutter.author_name }}$^{1}$\thanks{Email: \mailto{{{ cookiecutter.author_email }}}}\\
+    {{ cookiecutter.author_name }}$^{1}$\thanks{Email: \href{mailto:{{ cookiecutter.author_email }}}{ {{ cookiecutter.author_email.replace('_', '\_' ) }} } }\\
     $^{1}$ {{ cookiecutter.author_affiliation}}

### 2018-08-26 {{ cookiecutter.repo_name }}/Paper/paper.tex
Fixed typos

@@
 \hypersetup{
-    pdfauthor={{ cookiecutter.author_first_name + '_' + cookiecutter.author_last_name}},
+    pdfauthor={{ cookiecutter.author_name }},
     pdftitle={{ cookiecutter.paper_title}},
@@
 %% Author
-\author[{{ cookiecutter.author_last_name + 'et al. ' + cookiecutter.paper_pubyear}}]{
+\author[{{ cookiecutter.author_last_name + ' et al. ' + cookiecutter.paper_pubyear}}]{
     % Author List
